Improving the portuguese hyphenation rules

### 2023-07-13 article/article.tex
fix #15

The automation of this process might use a dictionary based approach, which
will restrict the hyphenation possibilities to those entries in the dictionary,
an algorithmic base approach, which might be applied to whatever sequence found
in a text, or a mix of bothe approaches. An algorithmic approach might use a
logic system to analyse words and apply the hyphenation rules of a given
language. A rule base model might include the recognition of prefixes,
suffixes, morphemes, or some sequences suitable for the inclusion of a break.
Another approach is the usage of pattern matching. Given a corpus of
hyphenation examples in a language, it is necessary to identify those sequence
of letters that define a point where hyphenation is suitable or not. Patterns
might include prefixes, suffixes, exceptions and special hyphenation rules of a
given language. Such approach might be used for different languages, by
providing hyphenation examples in a target language to extract patterns and
rules.

@@

Those rules are organized
in different levels, from 1 to 9, where odd numbers represent hyphenating
levels and even numbers represent inhibiting levels. Each level works as an
inhibiting level of it predecessor. A pattern will consist of a string made of
characters (from the language alphabet) possibly with a number in between,
expressing the hyphenation/inhibition level and possibly word boundaries marker
(the period) at the pattern edges. When there is no number between characters
in a pattern, a zero is assumed, which means \emph{undefined} and no
hyphenation point will be suggest at that location.

>>>>

The automation of this process might use a dictionary based approach, which
will restrict the hyphenation possibilities to those entries in the dictionary,
an algorithmic base approach, which might be applied to whatever sequence found
in a text, or a mix of both approaches. 
%An algorithmic approach might use a logic system to analyse words and apply
%the hyphenation rules of a given language. 
A rule base model might include the recognition of prefixes,
suffixes, morphemes, or some sequences suitable for the inclusion of a break.
Another approach is the usage of pattern matching. Given a corpus of
hyphenation examples in a language, it is necessary to identify those sequence
of letters that define a point where hyphenation is suitable or not. Patterns
might include prefixes, suffixes, exceptions and special hyphenation rules of a
given language. Such approach might be used for different languages, by
providing hyphenation examples in a target language to extract patterns and
rules.

@@

Those rules are organized
in different levels, from 1 to 9, where odd numbers represent hyphenating
levels and even numbers represent inhibiting levels. Each level works as an
inhibiting level of it predecessor. 
%A pattern will consist of a string made of
%characters (from the language alphabet) possibly with a number in between,
%expressing the hyphenation/inhibition level and possibly word boundaries marker
%(the period) at the pattern edges. When there is no number between characters
%in a pattern, a zero is assumed, which means \emph{undefined} and no
%hyphenation point will be suggest at that location.
